\large STRATEGIC SOCIAL LEARNING AND THE POPULATION DYNAMICS OF HUMAN BEHAVIOR: THE GAME OF GO

### 2022-06-23 manuscript.tex
misc tweaks

@@

>>>>

\title[STRATEGIC SOCIAL LEARNING]
{\large STRATEGIC SOCIAL LEARNING AND THE POPULATION DYNAMICS OF HUMAN BEHAVIOR:
THE GAME OF GO}
\author{Bret A. Beheim\(^1\), Calvin Thigpen\(^2\), Richard McElreath\(^3\)}
\address{\(^1\)Department of Anthropology, University of New Mexico.
\(^2\)Institute for Transportation Studies, University of California,
Davis. \(^3\) Department of Anthropology, University of California,
Davis}
\email{beheim@gmail.com}
\date{March 28, 2014}

@@

\maketitle
